### 2014-01-21 inst/doc/Advanced_parsing_of_EML.Rmd
update tutorial
rename package as EML instead of reml, closes #63

In [Advanced parsing and manipulation of EML](https://github.com/ropensci/reml/blob/master/inst/doc/Advanced_parsing_of_EML.md), we

@@

@@

```{r}
node@givenName <- John
```

@@

```{r}
slot(node, "givenName") <- John
```

>>>>

```{r include=FALSE, cache=FALSE}
source("~/.knitr_defaults.R")
```

In [Advanced parsing and manipulation of EML](https://github.com/ropensci/EML/blob/master/inst/doc/Advanced_parsing_of_EML.md), we

@@

```{r}
library(EML)
```

@@

```{r}
node@givenName <- "John"
```

@@

```{r}
slot(node, "givenName") <- "John"
```

### 2014-01-21 inst/doc/README.Rmd
rename package as EML instead of reml, closes #63

reml
====

@@

* **Note:** This package is still in active development and not yet submitted to CRAN.  Functions and documentation may be incomplete and subject to change.  
* Maintainer: Carl Boettiger
* Authors: Carl Boettiger, Duncan Temple Lang, Karthik Ram, Matt Jones
* License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
* [Issues](https://github.com/ropensci/reml/issues): Bug reports, feature requests, and development discussion.

_This is a dynamic document, generated by [knitr](http://yihui.name/knitr) using [vignette.Rmd](https://github.com/ropensci/reml/blob/master/inst/doc/vingette.Rmd) as the source._

@@

```{r, results="hide", message=FALSE, warning=FALSE, eval=FALSE}
library("devtools")
install_github("reml", "ropensci")
```

@@

```{r, results="hide", message=FALSE, warning=FALSE}
library("reml")
```

@@

`reml` now extends R's `data.frame` class by introducing the `data.set` class which includes additional metadata required by EML.  A `data.set` can be created much like a `data.frame` by specifying additional arguments

@@

```{r}
eml_write(dat, file = "reml_example.xml")
```

*for convenience, had we ommitted any essential metadata, such as providing only an unannotated `data.frame` in place of a `data.set`, `reml` will launch its metadata wizard to assist in constructing the metadata based on the data.frame provided*.  While this may be helpful starting out, regular users will find it faster to define the columns and units directly in the format above.

See the [EML generated](https://github.com/ropensci/reml/tree/master/inst/doc/reml_example.xml) by this example.

@@

```{r}
eml_validate("reml_example.xml")
```

* See [Open issues in writing EML](https://github.com/ropensci/reml/issues?labels=write+eml&page=1&state=open)

@@

_Note: this example assumes `rfigshare` is installed, even though it is not 
required to use reml and run the examples in the other sections.  See the 
`rfigshare` documentation for authenticating `rfigshare` with your user account_

@@

```{r publish_figshare} 
eml_publish("reml_example.xml", description="Example EML file from reml", categories = "Ecology", tags = "EML", destination="figshare")
```

@@

See [Open issues in publishing EML](https://github.com/ropensci/reml/issues?labels=publish+eml&page=1&state=open)

@@

```{r}
obj <- eml_read("reml_example.xml")
```

@@

While the dependencies for basic functionality are kept to a minimum, to access all the functions and tests implemented in `reml` you'll need several additional packages.

@@

***Suggestions, feature requests, bug reports and other feedback welcome!*** Please see our [issues tracker](https://github.com/ropensci/reml/issues)

>>>>

EML
====

@@

* **Note:** This package is still in active development and not yet submitted to CRAN.  Functions and documentation may be incomplete and subject to change.  
* Maintainer: Carl Boettiger
* Authors: Carl Boettiger, Claas-Thido Pfaff, Duncan Temple Lang, Karthik Ram, Matt Jones
* License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
* [Issues](https://github.com/ropensci/EML/issues): Bug reports, feature requests, and development discussion.

_This is a dynamic document, generated by [knitr](http://yihui.name/knitr) using [vignette.Rmd](https://github.com/ropensci/EML/blob/master/inst/doc/vingette.Rmd) as the source._

@@

```{r, results="hide", message=FALSE, warning=FALSE, eval=FALSE}
library("devtools")
install_github("EML", "ropensci")
```

@@

```{r, results="hide", message=FALSE, warning=FALSE}
library("EML")
```

@@

`EML` now extends R's `data.frame` class by introducing the `data.set` class which includes additional metadata required by EML.  A `data.set` can be created much like a `data.frame` by specifying additional arguments

@@

```{r}
eml_write(dat, file = "EML_example.xml")
```

*for convenience, had we ommitted any essential metadata, such as providing only an unannotated `data.frame` in place of a `data.set`, `EML` will launch its metadata wizard to assist in constructing the metadata based on the data.frame provided*.  While this may be helpful starting out, regular users will find it faster to define the columns and units directly in the format above.

See the [EML generated](https://github.com/ropensci/EML/tree/master/inst/doc/EML_example.xml) by this example.

@@

```{r}
eml_validate("EML_example.xml")
```

* See [Open issues in writing EML](https://github.com/ropensci/EML/issues?labels=write+eml&page=1&state=open)

@@

_Note: this example assumes `rfigshare` is installed, even though it is not 
required to use EML and run the examples in the other sections.  See the 
`rfigshare` documentation for authenticating `rfigshare` with your user account_

@@

```{r publish_figshare} 
eml_publish("EML_example.xml", description="Example EML file from EML", categories = "Ecology", tags = "EML", destination="figshare")
```

@@

See [Open issues in publishing EML](https://github.com/ropensci/EML/issues?labels=publish+eml&page=1&state=open)

@@

```{r}
obj <- eml_read("EML_example.xml")
```

@@

While the dependencies for basic functionality are kept to a minimum, to access all the functions and tests implemented in `EML` you'll need several additional packages.

@@

***Suggestions, feature requests, bug reports and other feedback welcome!*** Please see our [issues tracker](https://github.com/ropensci/EML/issues)

### 2014-01-21 inst/doc/knb.Rmd
rename package as EML instead of reml, closes #63

_Note: this example assumes `dataone` is installed, even though it is not 
required to use reml and run the examples in the other sections.  See the 
`dataone` documentation for authenticating `dataone` with a user account_

```{r publish_knb}
ids <- eml_publish("reml_example.xml", destination="KNB", permanent=FALSE)
```

>>>>

_Note: this example assumes `dataone` is installed, even though it is not 
required to use EML and run the examples in the other sections.  See the 
`dataone` documentation for authenticating `dataone` with a user account_

```{r publish_knb}
ids <- eml_publish("EML_example.xml", destination="KNB", permanent=FALSE)
```

### 2014-01-21 inst/doc/one-simple-way.Rmd
rename package as EML instead of reml, closes #63

Use `reml`.

@@

Sharing is as easy as `publish_reml("my_eml_data.xml")`

@@

`reml` can automatically push our data to a variety of established repositories, as illustrated in this example.

@@

We see by default `reml` has provided us with the liberal CC0 license for the data, consistent with major repositories such as Dryad.  Other options can be specified if needed.

>>>>

Use `EML`.

@@

Sharing is as easy as `publish_EML("my_eml_data.xml")`

@@

`EML` can automatically push our data to a variety of established repositories, as illustrated in this example.

@@

We see by default `EML` has provided us with the liberal CC0 license for the data, consistent with major repositories such as Dryad.  Other options can be specified if needed.
